---
title: "R Character Manipulation and Date Processing"
author: "Subhalaxmi Rout"
date: "2/16/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

### Answer
```{r eval=TRUE, load-data}
data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", TRUE,",")
head(data$Major)
grep("DATA",data$Major, value = T)
grep("STATISTICS",data$Major, value = T)
```

### 2 Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

### Answer
```{r}
library("stringr")
food <- '"bell pepper"  "bilberry"     "blackberry"   "blood orange"
 "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
 "elderberry"   "lime"         "lychee"       "mulberry"    
 "olive"        "salal berry"'
food <- str_extract_all(food, '[a-z]+\\s[a-z]+|[a-z]+')
food
```

### 3 Describe, in words, what these expressions will match:

+ (.)\1\1
+ "(.)(.)\\2\\1"
+ (..)\1
+ "(.).\\1.\\1"
+ "(.)(.)(.).*\\3\\2\\1"

### Answer
```
(.)\1\1: same charecter 3 times.
example: "sss"

"(.)(.)\\2\\1": 2 charecters repeat in reverse way.
Example: "bccb"

(..)\1: any 2 charecters repeated.
Example: "abab"

"(.).\\1.\\1": 1st charecter followed by another charecter, 
             again 1st charecter followed by other charecter,repeated 3 times.
Example: "abacad"

"(.)(.)(.).*\\3\\2\\1": 3 charecter followed by zero or more charecter 
                      then same 3 charecter but in reverse way. 
Example: "abc12cba"

```

### #4 Construct regular expressions to match words that:

+ Start and end with the same character.
+ Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
+ Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

### Answer
``` {r}
# Start and end with the same character.
words = c("ruler", "salsa", "environmental")
str1 <- str_subset(words, "^(.)((.*\\1$)|\\1?$)")
str1

# Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
str2 <- str_subset(words, "([a-z]{2})[a-z].*\\1")
str2

# Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
str3 <- str_subset(words, "([a-z]).*\\1.*\\1")
str3
```